---
title: "Reproducible Research: Peer Assessment 1"
author: Oliver Gonzalez
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
1)Load the data
  unzip("activity.zip")
  activity <- read.csv("activity.csv",header = TRUE, sep=',')

2)Process/transform the data (if necessary) into a format suitable for your analysis
  activity$date<-ymd(activity$date)
  str(activity)
  head(activity)
```
## What is mean total number of steps taken per day?
```{r}
1)Calculate the total number of steps per day and group by date:
  steps_day<- activity %>%
      filter(!is.na(steps)) %>%
      group_by(date) %>%
      summarize(dly_steps = sum(steps)) %>%
    
2)Using ggplot for making hystogram    
    graph1<-ggplot(steps_day,aes(x=dly_steps))+geom_histogram( boundary=0,col="darkblue",fill="darkgreen",binwidth = 1200) +
      labs(title = "Histogram of Steps per day", x = "Steps per day", y =        "Frequency")+scale_x_continuous(breaks=seq(0,25000,2500))+scale_y_continuous(breaks=seq(0,26,2))
 
3)Calculate the mean and median of the total number of steps taken per day:
  mean_steps <- mean(steps_day$dly_steps, na.rm = TRUE)
  median_steps <- median(steps_day$dly_steps, na.rm = TRUE)
```

## What is the average daily activity pattern?
1)Calculate the average number of steps taken in each 5-minute interval per day and group by interval:
  interval <- activity %>%
    filter(!is.na(steps)) %>%
    group_by(interval) %>%
    summarize(steps_interval = mean(steps))
  using ggplot for making the time series of the 5-minute interval, and the avergae of steps
  ggplot(interval, aes(x=interval, y=steps_interval)) +
  geom_line(color = "firebrick")
 2)Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
    interval[which.max(interval$steps),]
    
## Imputing missing values
1)Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
  sum(is.na(activity$steps))

## Are there differences in activity patterns between weekdays and weekends?
